\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-07 psharp.tex
updates in async/await

As an example, the Live Azure Migration system uses the \texttt{async} and \texttt{await} \csharp \PDComment{version} language primitives. Asynchronous code using async/await is more readable because it looks like traditional procedural code, but it is translated by the compiler to an event-driven state machine that is built on top of TPL to achieve performance.

\PDComment{small example of how async/await actually works with continuations}

>>>>

As an example, the Live Azure Migration system uses the \texttt{async} and \texttt{await} \csharp 5.0 language primitives. Asynchronous code using \texttt{async}/\texttt{await} is more readable because it looks like traditional procedural code, but it is translated by the compiler to an event-driven state machine that is built on top of TPL to achieve performance. The key idea behind \texttt{async}/\texttt{await} is that a method declared as \texttt{async} can use internally the \texttt{await} keyword which allows the thread executing the method to wait on a TPL task, or any other \emph{awaitable} object, \emph{without} blocking. This is achieved as follows. When an \texttt{await} statement is executed, the code following the await is wrapped as a TPL task \emph{continuation} and the method returns to the caller. This continuation executes when the awaitable object has completed.
